Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-13 Paper/paper.tex
Trying to work on multiple laptops always causes issues....
Edits and fixes. Working on two computers is a pain
Kurfess Edits

\usepackage{titlesec}

@@

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others\cite{EvolutionOfWeb}. In that same time period, the number of global internet users has grown to somewhere around two and a half billion\cite{EvolutionOfWeb}. The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on\cite{ErrorsInTheWild}. That may seem like a incredibly small amount for such monoliths but every error is an opportunity for malfunction and customer dissatisfaction.

@@

Even the tools that already exist suffer from additional problems regarding their stages of development and amount of support. As will be discussed later, we've found tools that are in their beta stages that show incredible promise as well as mature tools that are widely used but leave much to be desired. These problems effect both industry tools as well as independent developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators\cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

@@

\subsection{Versioning}
Web applications can be updated at any time with instant roll-out and feedback. It requires absolutely no user interaction because the web page always serves the latest resources. In comparison to something like Microsoft Office that requires users to manually update, this feature leads to applications that can address problems quickly, roll-out security updates instantly, and incorporate consumer feedback much more often than any other type of software. For example, Google Docs is becoming incredibly popular as an online document editing suite. Updates to Google Docs are rolled out frequently and require little to no input from the user. Another perk is that users are not given a choice. This can lead to occasional customer outrage, but more often than not it is a powerful gain for both feature improvement and application security. There is no need to support legacy systems that may contain serious bugs.

@@

\subsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality. Nearly all devices made today come equipped with browsers that support the necessary functionality. This also means that the developer need not, generally, worry about hardware configurations, conflicting software, and other problems that can arise in desktop applications.

The developer is not free from all worry as they must still consider differing web browsers. This problem, however, is almost fully remedied by a number of online APIs, such as jQuery\cite{jQuery}, that will rework underlying code based on browser versions and types.

@@

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox back in 2009\cite{EvolutionOfWeb}. HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014\cite{Plan2014}. What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

The HTML5 specification brings with it a number of new features including: audio and video tags, the canvas element, drag-and-drop functionality, web storage, offline page support, and a number of other modern web features. A lot of HTML5's features revolve around the inclusion of multimedia in web pages and stronger graphical processing and programming. HTML5 is a collection of new HTML elements and markup as well as libraries written in Javascript.

@@

JavaScript, though not the only scripting language with web use, is the primary language used to compliment HTML5 when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an iterative environment.

@@

Node is found in a number of popular sites including: PayPal, The New York Times, Yahoo!, Uber, LinkedIn, Microsoft Azure, and a number of others\cite{Node}.

One of the biggest draws of Node.js is the ability to write all of one's code, client and server, in a single programming language, Javascript. This leads to better understanding of the codebase as well as the opportunity for code reuse between client and server.

@@

Clients communicate with the Server through a request-response architecture. Clients send a request to the server, often with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.

One example of a client-server architecture that is popular for the web is the Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base URI, 2) an internet media type, and 3) the standard HTTP methods.

@@

\subsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' According to IEEE, test units are ``[a] set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures that satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.''\cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

function testMakePluralCheckPartOfSpeech () { ... } // Not a Unit test, testing multiple units

@@

Unit tests are important because they are done in isolation from one another. The purpose of a unit test is to ensure that once individual modules are put together, the developer need only focus on the interaction between them instead of their individual functionality. Without the assurances of prior unit tests, integration would be a more stressful and mysterious proposition.

\subsection{Integration Testing}
After writing Unit tests, a developer writes Integration tests. Integration tests are used to determine if modules work together to produce correct results. In our previous example, this would mean testing most of the \lstinline{Sentence} functions to ensure that they properly use the \lstinline{Word}s that the \lstinline{Sentence} contains. Integration Tests cover a wider variety of test situations from single methods to entire modules.

Integration Testing is important because it gives the developer a sense of what modules are actually producing correct results, as opposed to which modules are functioning as anticipated. This distinction is critical to make. Unit Tests ensure that individual modules function. Integration tests are usually written in a way that is close to how they will actually be used in the final product, giving the developer a sense of which features are working and which are not.

\subsection{Continuous Integration}
The original definition of Continuous Integration involves the idea of developers committing from their  branches to a master branch daily so that changes are continuously integrated in an effort to make sure all branches can, in fact, be integrated. It has since evolved into a more general idea of a tool that runs commands after each commit to a repository. These commands generally encompass running unit tests, integration tests, user interface tests, and also often publishing and disseminating notifications to interested parties. This is invaluable feedback because the developer can see if they're making progress in the right direction as they write code, as opposed to a situation in which the developer finishes coding and finds out they've made a bad assumption or decision between this commit and the last.

@@

\subsection{Acceptance Testing}
Acceptance testing is testing to confirm that the product meets a certain specification. Often this is making sure that the software meets an SRS (Software Requirements Specification) or a customer's outlined expectations. Often this testing is performed by the user of the software or customer that ordered the software, rather than the developers.

@@

\subsection{Testing Statistics}
It is widely accepted that the earlier a developer detects a defect, the easier it is to fix that defect. A famous book, ``Code Complete'' by Steve McConnell\cite{DefectPic}, includes the following figure, showing this statistic on a rough graph.

@@

% - CONSIDER REMOVING ALTOGETHER
% \subsection{Why Testing is Important}
% We're consistently surprised by how few people take testing seriously when it comes to non-trivial applications. Many developers will leave testing to their users, i.e., wait for users to have problems and report them before developers will fix them. This is an issue for a number of reasons, a few of which are: frustrated customers are unlikely to continue using a buggy product and are dissuaded from buying future products from the same developer, certain bugs can be security loopholes that may allow users access to information they shouldn't have, in the worst cases a bug may cause damage to a person or property and the developers would be on the hook.

@@

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB\cite{ToDoAppHomePage}. Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, marking tasks as completed, and viewing completed tasks. Here is a brief preview of the application's UI:

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png}

\captionof{figure}{ToDo app home page, simple three-button naviagation}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_some_tasks.png}

\captionof{figure}{ToDo app task page}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_completed.png}

\captionof{figure}{ToDo app completed tasks page}

\end{Figure}

@@

\subsection{The Average Web Application}
In an effort to create a detailed and in-depth workflow and collection of tools, we have chosen to focus on web applications that use Node.js, JavaScript, and a backing Database. Although this will not cover all web application configurations, we wanted to narrow our scope in order to provide a specific, instead of general, set of guidelines and workflow suggestions.

@@

JavaScript is the language of HTML5 and Node.js. It is used in over 87\% of all websites\cite{JSUsage} and as such allows us to create a workflow to cover a majority of web applications.

@@

\section{Unit Testing Frameworks}
The following frameworks are reviewed in chronological order of our evaluation. As such, comparisons will generally only be drawn between a framework and its predecessors in paper order. After all of the frameworks are outlined and evaluated, a section regarding the final decision will be made where comparisons will be drawn between all of them.

Web applications can be broken down into two general parts. There is functionality behind the scenes that drives the web page and there is the user interface of the web page that conveys the information to the user. Unit testing frameworks are aimed at the functionality the drives the web page, not what the user sees.

\subsection{Jasmine}
The first of the unit testing frameworks that we looked at was Jasmine\cite{Jasmine}, a Behavior Driven Development (BDD) testing framework. BDD is based on Test Driven Development and adds some simplifications and patterns that attempt to bring both developers and businessmen into the software testing process. The idea behind Behavior Driven Development is that input from non-technical stakeholders as well as technical stakeholders can come together so that everyone understands what the project should do.

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

The default Jasmine did not support Node.js but there was a package available through npm called jasmine-node\cite{JasmineNode} that gave jasmine access to the node package and functions.

@@

\subsection{Mocha}
Mocha\cite{Mocha} is another BDD testing framework that is almost identical to Jasmine. Unlike Jasmine, however, Mocha is not completely self-contained and requires an additional assertion library of one's choosing. We will outline our choice of Chai.js below.

Mocha, by default, also uses the \lstinline{describe -> it("should..."} pattern to create tests. Mocha offers a variety of other test interfaces for developers to write their test code. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

\subsubsection{Chai.js}
For the assertion library we chose Chai.js\cite{Chaijs}. It contains three different assertion APIs: an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions of the form \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to an experience that can appeal to a variety of different developers.

\subsection{QUnit}
QUnit\cite{QUnit} is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, a popular framework for DOM manipulation and access\cite{jQuery}. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png}
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}

An interesting feature that QUnit has is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. Silent failure can happen if the developer forgets to specify that a test is asynchronous or if there are synchronous callbacks. If a function in the test has a callback that runs the assertions, the test framework may finish executing the test and move on to the next test before ever running the assertions in the callback. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

QUnit tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

\subsection{Intern}
Intern\cite{InternIO} is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. It is our intention to build a testing framework with all of these components, so finding a framework with all of them built-in was promising. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of our inability to set up cross-server communication due to inexperience.

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas\cite{AMDInfo}. Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because that is what Node.JS uses, which is used by our evaluation applications.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran\cite{Istanbul}.

@@

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

Selenium was written with maximum functionality and language flexibility in mind and therefore can be incredibly verbose.

@@

\subsection{Nightwatchjs}
Nightwatch\cite{NightwatchJS} is a JavaScript testing library built on top of Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

Nightwatch is a Node.js module, and as such can easily installed and run via npm and the commandline.

@@

\subsubsection{PhantomJS}
PhantomJS\cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

There are, however, a couple problems with PhantomJS. It is generally fairly verbose when it comes to writing the scripts that run your commands. It is also not a testing tool, it is a headless WebKit. The distinction here is that PhantomJS does not have any assert functionality built-in and thus requires the developer to find and use their own assertion library.

@@

\subsubsection{ZombieJS}
ZombieJS\cite{ZombieJS} is the other headless browser that we saw when searching for browser testing tools. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

Developers like ZombieJS syntax so much that there exists a wrapper that uses ZombieJS's API around PhantomJS\cite{ZombiePhantom}.

@@

Manual CI is incredibly similar to Jenkins in that its only limitations are the libraries and hardware that the scripts are run on.

>>>>

\usepackage{titlesec}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue
}

@@

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others \cite{EvolutionOfWeb}. In that same time period, the number of global internet users has grown to somewhere around two and a half billion \cite{EvolutionOfWeb}. The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications and websites around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on \cite{ErrorsInTheWild}. That may seem like a small amount for such large sites, but every error is an opportunity for malfunction and customer dissatisfaction.

@@

Even the tools that already exist suffer from additional problems regarding their stages of development and amount of support. As will be discussed later, we've found tools that are in their beta stages that show incredible promise as well as mature tools that are widely used but leave much to be desired. These problems affect both industry tools as well as independent developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\section{Web Application Definition}
The difference between a website and web application is hard to precisely define, but it comes down to the user's and developer's intentions. A website is an online set of documents whose purpose is mainly informational. A web application is an online set of documents whose purpose is functional. Compare a website like CNN with with a web application like Google Drive and the difference is striking. On the other hand, thinking of a web page like Google it's tougher to make the distinction. Although Google is used as an information gathering tool, it has incredible functionality behind its search box and so we consider it to be an application. If a web page, or pages, is either highly functional or requires significant behind the scenes functionality, the web page is considered an application. If the page, or pages, is informational and does not have significant processing power, it is a website.

@@

\subsection{Versioning}
Web applications can be updated at any time with instant roll-out and feedback. It requires absolutely no user interaction because the web page always serves the latest resources. In comparison to something like Microsoft Office that requires users to manually update, this feature leads to applications that can address problems quickly, roll-out security updates instantly, and incorporate consumer feedback much more often than any other type of software. For example, Google Docs is becoming popular as an online document editing suite. Updates to Google Docs are rolled out frequently and require little to no input from the user. Another perk is that users are not given a choice. This can lead to occasional customer outrage, but more often than not it is a powerful gain for both feature improvement and application security. There is no need to support legacy systems that may contain serious bugs.

@@

\subsection{Multi-device}
Very similar to the availability strength, web applications are device independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality. Nearly all devices made today come equipped with browsers that support the necessary functionality. This also means that the developer need not, generally, worry about hardware configurations, conflicting software, and other problems that can arise in desktop applications.

The developer is not free from all worry as they must still consider differing web browsers. This problem, however, is almost fully remedied by a number of online APIs, such as jQuery \cite{jQuery}, that will rework underlying code based on browser versions and types.

@@

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox back in 2009 \cite{EvolutionOfWeb}. HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014 \cite{Plan2014}. What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

The HTML5 specification brings with it a number of new features including: audio and video tags, the canvas element, drag-and-drop functionality, web storage, offline page support, and a number of other modern web features. A lot of HTML5's features revolve around the inclusion of multimedia in web pages and stronger graphical processing and programming. HTML5 is a collection of new HTML elements and markup as well as libraries written in JavaScript.

@@

JavaScript, though not the only scripting language with web use, is the primary language used to complement HTML5 when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an iterative environment.

@@

Node is found in a number of popular sites including: PayPal, The New York Times, Yahoo!, Uber, LinkedIn, Microsoft Azure, and a number of others \cite{Node}.

One of the biggest draws of Node.js is the ability to write all of one's code, client and server, in a single programming language, JavaScript. This leads to better understanding of the codebase as well as the opportunity for code reuse between client and server.

@@

Clients communicate with the server through a request-response architecture. Clients send a request to the server, often with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.

One example of a client-server architecture that is popular for the web is the Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base uniform resource identifier (URI), 2) an internet media type, and 3) the standard HTTP methods.

@@

\subsection{Unit Testing}
Unit Testing is the testing of specific functions and functionality, or ``test units.'' According to IEEE, test units are ``[a] set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures that satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.''\cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

function testMakePluralCheckPartOfSpeech () { ... } // Not a Unit Test, testing multiple units

@@

Unit Tests are important because they are done in isolation from one another. The purpose of a Unit Test is to ensure that once individual modules are put together, the developer need only focus on the interaction between them instead of their individual functionality. Without the assurances of prior Unit Tests, integration would be a more stressful and mysterious proposition.

\subsection{Integration Testing}
After writing Unit Tests, a developer writes Integration Tests. Integration Tests are used to determine if modules work together to produce correct results. In our previous example, this would mean testing most of the \lstinline{Sentence} functions to ensure that they properly use the \lstinline{Word}s that the \lstinline{Sentence} contains. Integration Tests cover a wider variety of test situations from single methods to entire modules.

Integration Testing is important because it gives the developer a sense of what modules are actually producing correct results, as opposed to which modules are functioning as anticipated. This distinction is critical to make. Unit Tests ensure that individual modules function. Integration Tests are usually written in a way that is close to how they will actually be used in the final product, giving the developer a sense of which features are working and which are not.

\subsection{Continuous Integration}
The original definition of Continuous Integration (CI) involves the idea of developers committing from their  branches to a master branch daily so that changes are continuously integrated in an effort to make sure all branches can, in fact, be integrated. It has since evolved into a more general idea of a tool that runs commands after each commit to a repository. These commands generally encompass running Unit Tests, Integration Tests, user interface tests, and also often publishing and disseminating notifications to interested parties. This is invaluable feedback because the developer can see if they're making progress in the right direction as they write code, as opposed to a situation in which the developer finishes coding and finds out they've made a bad assumption or decision between this commit and the last.

@@

\subsection{Acceptance Testing}
Acceptance Testing is testing to confirm that the product meets a certain specification. Often this is making sure that the software meets an SRS (Software Requirements Specification) or a customer's outlined expectations. Often this testing is performed by the user of the software or customer that ordered the software, rather than the developers.

@@

\subsection{Testing Statistics}
It is widely accepted that the earlier a developer detects a defect, the easier it is to fix that defect. A famous book, ``Code Complete'' by Steve McConnell \cite{DefectPic}, includes the following figure, showing this statistic on a rough graph.

@@

@@

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB \cite{ToDoAppHomePage}. This application was an open-source application available online. Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, marking tasks as completed, and viewing completed tasks. Here is a brief preview of the application's UI:

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png} 
  \captionof{figure}{ToDo app home page, simple three-button naviagation} 
\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_some_tasks.png}  
  \captionof{figure}{ToDo app task page}  
\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_completed.png} 
  \captionof{figure}{ToDo app completed tasks page}
\end{Figure}

@@

\subsection{The Average Web Application}
In an effort to create a detailed and in-depth workflow and collection of tools, we have chosen to focus on web applications that use Node.js, JavaScript, and a backing database. Although this will not cover all web application configurations, we wanted to narrow our scope in order to provide a specific, instead of general, set of guidelines and workflow suggestions.

@@

JavaScript is the language of HTML5 and Node.js. It is used in over 87\% of all websites \cite{JSUsage} and as such allows us to create a workflow to cover a majority of web applications.

@@

\section{Unit Testing Frameworks}
The following frameworks are reviewed in chronological order of our evaluation. There was no determined order in whcih we evaluated them. As such, comparisons will generally only be drawn between a framework and its predecessors in paper order. After all of the frameworks are outlined and evaluated, a section regarding the final decision will be made where comparisons will be drawn between all of them.

Web applications can be broken down into two general parts. There is functionality behind the scenes that drives the web page and there is the user interface of the web page that conveys the information to the user. Unit Testing frameworks are aimed at the functionality that drives the web page, not what the user sees.

\subsection{Jasmine}
The first of the Unit Testing frameworks that we looked at was Jasmine \cite{Jasmine}, a Behavior Driven Development (BDD) testing framework. BDD is based on Test Driven Development and adds some simplifications and patterns that attempt to bring both developers and businessmen into the software testing process \cite{BDD}. The idea behind Behavior Driven Development is that input from non-technical stakeholders as well as technical stakeholders can come together so that everyone understands what the project should do \cite{BDD}.

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind Jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

The default Jasmine did not support Node.js but there was a package available through NPM called jasmine-node \cite{JasmineNode} that gave Jasmine access to the node package and functions.

@@

\subsection{Mocha}
Mocha \cite{Mocha} is another BDD testing framework that is almost identical to Jasmine. Unlike Jasmine, however, Mocha is not completely self-contained and requires an additional assertion library of one's choosing. We will outline our choice of Chai.js below.

Mocha, by default, also uses the \lstinline{describe -> it("should...", ...)} pattern to create tests. Mocha offers a variety of other test interfaces for developers to write their test code. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

\subsubsection{Chai.js}
For the assertion library we chose Chai.js \cite{Chaijs}. It contains three different assertion APIs: an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions of the form \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to an experience that can appeal to a variety of different developers.

\subsection{QUnit}
QUnit \cite{QUnit} is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, a popular framework for Document Object Model (DOM) manipulation and access \cite{jQuery}. The DOM is a convention for interacting with objects in HTML, XHTML, and XML documents. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png}
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}

An interesting feature that QUnit has is the ability to specify how many assertions are expected to run in the test. This is useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. Silent failure can happen if the developer forgets to specify that a test is asynchronous or if there are synchronous callbacks. If a function in the test has a callback that runs the assertions, the test framework may finish executing the test and move on to the next test before ever running the assertions in the callback. If the QUnit Test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

QUnit Tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

\subsection{Intern}
Intern \cite{InternIO} is a hybrid Unit Testing and browser testing framework that aims to be an all-in-one testing framework. Intern has Unit Testing, browser testing, and code coverage information all built into the same tool. It is our intention to build a testing framework with all of these components, so finding a framework with all of them built-in was promising. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of our inability to set up cross-server communication due to inexperience.

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas \cite{AMDInfo}. Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because that is what Node.JS uses, which is used by our evaluation applications.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running Unit Tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

\subsection{Selenium}
Selenium \cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

Selenium was written with maximum functionality and language flexibility in mind and therefore can be verbose.

@@

\subsection{Nightwatchjs}
Nightwatch \cite{NightwatchJS} is a JavaScript testing library built on top of Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

Nightwatch is a Node.js module, and as such can easily installed and run via NPM and the commandline.

@@

\subsubsection{PhantomJS}
PhantomJS \cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

There are, however, a couple of problems with PhantomJS. It is generally fairly verbose when it comes to writing the scripts that run your commands. It is also not a testing tool, it is a headless WebKit. The distinction here is that PhantomJS does not have any assert functionality built-in and thus requires the developer to find and use their own assertion library.

@@

\subsubsection{ZombieJS}
ZombieJS \cite{ZombieJS} is the other headless browser that we saw when searching for browser testing tools. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

Developers like ZombieJS syntax so much that there exists a wrapper that uses ZombieJS's API around PhantomJS \cite{ZombiePhantom}.

@@

Manual CI is similar to Jenkins in that its only limitations are the libraries and hardware that the scripts are run on.
